---
title: "Programming Assignment 4"
subtitle: 
author: "Jessyca Campos"
date: "March 6, 2018"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# Load the dataset

```{r, load_data, message=FALSE}

library(tidyverse)
my_data <- read.csv('../data_raw/fricatives/fricatives.csv')
str(my_data)
head(my_data)

```

---

# Tidy the dataset

```{r, tidy_data }
tidydata <- my_data %>%
  gather(., measurement, value, -obs) %>%
  separate(., measurement, into = c('phoneme', 'measure'), sep = '_') %>%
  spread(., key = measure, value = value)
  head(tidydata)
```

---

# Descriptive stats

```{r, stats }
tidydata %>% 
  group_by(., phoneme) %>% 
  summarize(., mean_cog = mean(cog),
               sd_cog = sd(cog), 
               mean_skewness = mean(skewness),
               sd_skewness = sd(skewness)) %>%
  knitr::kable(., format = 'html', digits = 2)
```

---

# Boxplot: center of gravity ~ phoneme

```{r, boxplot, fig.width=8, echo=FALSE}
tidydata %>%
  ggplot(., aes(x = phoneme, y = cog, fill = phoneme)) +
  geom_boxplot(width = 0.4)
```

---

# Plot: skewness ~ phoneme

```{r, plot, fig.width=8, echo=FALSE}
tidydata %>%
  ggplot(., aes(x = phoneme, y = skewness)) +
  stat_summary(fun.data = mean_cl_boot, 
               geom = 'pointrange', shape = 1)
```

---

# Model: center of gravity ~ skewness for [s]

```{r, model}
s_fit <- tidydata %>%
  filter(., phoneme == 's')

tidydata_fit <- lm(skewness ~ cog, data = s_fit)
summary(tidydata_fit)
```

---

# Model summary table

```{r, }

broom::tidy(tidydata_fit) %>%
  knitr::kable(., format = 'html', digits = 2)
```

---

# Scatterplot: center of gravity ~ skewness

```{r, scatterplot, fig.width=8, echo=FALSE}
tidydata_fit %>%
  ggplot(., aes (x = skewness, y = cog)) + 
  geom_point() + 
  geom_smooth(method = lm)
```

---

# Model diagnostics
---

# Check if association is linear
```{r, mod_diagnostics1, fig.width=8}
tidydata %>%
  ggplot(., aes(x = skewness, y = cog), fill = phoneme) +
  geom_point()

```

---

# Check if the mean of the residuals is zero

``` {r, }
mean(tidydata_fit$residuals)
summary(tidydata_fit)
```

---
# Check correlation of residuals

```{r, fig.align=8}
lmtest::dwtest(tidydata_fit)
```

---
```{r, resid_cont}
acf(tidydata_fit$residuals)
```

---

# Results

The data was analyzed using a linear model to assess the relationship between the skewness and the center of gravity of two fricatives [s] and [ʃ]. The model showed a positive linear relationship between center of gravity (cog) and skewness for the [s]. The model showed that the association between predictors was linear. The mean of the residuals was zero. Correlation of the residuals indicated a p-value less than 0.01 which suggests that it is significant.




















